---
title: "Reproducible pipelines from one-line target factories"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducible pipelines from one-line target factories}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

PhysioPipe is a collection of [`targets`](https://docs.ropensci.org/targets/)
**target factories** for the Physio ecosystem. Each factory returns a *list of
target objects* for one standard analysis, so a whole reproducible `_targets.R`
is a couple of lines and you still get `targets`' incremental re-runs and
byte-level provenance.

This vignette builds factories and inspects the target objects they produce. It
does **not** run a pipeline (`tar_make()`), which would need the ecosystem
analysis packages and, for a report, the Quarto CLI.

```{r setup}
library(PhysioPipe)
library(targets)
```

## A factory returns target objects

`tar_ecg_hrv()` expands to the standard resting-ECG HRV pipeline
(`read -> lead -> R-peaks -> RR -> {HRV time, HRV freq} -> summary`, plus a
tachogram figure and a Parquet export):

```{r ecg}
ecg <- tar_ecg_hrv()
length(ecg)
vapply(ecg, function(t) t$settings$name, character(1))
```

Each element is a `targets` target object:

```{r classes}
class(ecg[[1]])
```

A real `_targets.R` just splices the list in:

```{r targets-file, eval = FALSE}
# _targets.R
library(targets)
library(PhysioPipe)
list(
  tar_ecg_hrv()                               # bundled demo record
)
# then, at the console:  targets::tar_make()
```

## The single-modality factories

EEG band power, EMG amplitude/fatigue, and EDA skin-conductance each have a
factory. With `source = NULL` they point at a seeded *synthetic* signal so the
pipeline runs out of the box; pass an expression to read real data instead.

```{r modalities}
lengths(list(
  eeg = tar_eeg_bandpower(),
  emg = tar_emg_features(),
  eda = tar_eda_scr()
))

# Point a factory at a real file:
# tar_eeg_bandpower(source = quote(PhysioIO::readEDF("sub01.edf")))
```

## Cohorts fan out automatically

Give `tar_ecg_hrv()` several record bases and it switches to dynamic branching
(one branch per record) and adds a combined cohort table:

```{r cohort}
length(tar_ecg_hrv(records = c("data/100", "data/101", "data/102")))
```

## Synthetic demo data and pure helpers

`pp_simulate()` makes a clearly-synthetic `PhysioExperiment` for exercising a
pipeline's mechanics (not for making claims):

```{r simulate, eval = requireNamespace("PhysioCore", quietly = TRUE)}
pe <- pp_simulate("eeg")
pe
```

Small pure helpers assemble pipeline outputs -- e.g. stacking per-record cohort
branches into one table:

```{r helper}
pp_bind_cohort(
  list(data.frame(sdnn = 50), data.frame(sdnn = 61)),
  id = c("rec100", "rec101")
)
```

## Where to go next

* `?tar_ecg_hrv`, `?tar_eeg_bandpower`, `?tar_emg_features`, `?tar_eda_scr` --
  the single-modality factories.
* `?tar_physio_report` -- a Quarto report target (needs `tarchetypes` + Quarto).
* `?pp_write_parquet` -- the language-neutral interchange seam that keeps a
  pipeline orchestrator-agnostic.
